A meta-analysis of fungicide effects on mungbean powdery mildew

### 2021-05-21 04_Severity_MetaAnalysis.Rmd
Update model estimates table with results from logit model

intercept <- PMsev_mvSQ$b[1,1]

# create data.frame
results_mv <- data.frame(
   Moderator = c(
      "Intercept / No Spray control",
      "Early",
      "Late",
      "Late+",
      "Recommended",
      "Recommended+"
   ),
   N = k5,
   k = k6,
   Effect = ifelse(PMsev_mvSQ$b == intercept, sqrt(intercept),
                   round(
                      sqrt(PMsev_mvSQ$b + intercept) - sqrt(intercept), 4
                   )),
   se = round(
      sqrt(
         ifelse(PMsev_mvSQ$b == intercept, intercept,
                PMsev_mvSQ$b + intercept) + PMsev_mvSQ$se) -
         sqrt(
            ifelse(PMsev_mvSQ$b == intercept, intercept,
                   PMsev_mvSQ$b + intercept)),
      4),
   CI_lower = round(sqrt(PMsev_mvSQ$ci.lb + intercept) - sqrt(intercept), 4),
   CI_upper = round(sqrt(PMsev_mvSQ$ci.ub + intercept) - sqrt(intercept), 4),
   z_val = round(PMsev_mvSQ$zval, 4),
   p_val = reportP(PMsev_mvSQ$pval, AsNumeric = FALSE, P_prefix = FALSE))

results_mv <- 
   results_mv %>%
   mutate(
   eff_bar = round(
      1 - (sqrt(intercept) + Effect) /
              sqrt(intercept), 
      4) * 100,
   eff_CI_high = round(
      1 - (sqrt(intercept) + CI_upper) / sqrt(intercept)
   , 4) * 100,
   eff_CI_low = round(
      1 - (sqrt(intercept) + CI_lower) / sqrt(intercept)
   , 4) * 100

@@

# rename colnames to give table headings
colnames(results_mv)[c(1:4,6:12 )] <-
   c("Moderator",
     "N",
     "k",
     "mu",
     "CI_{L}",
     "CI_{U}",
     "Z",
     "P",
     "Efficacy",
     "Eff CI_lower",
     "Eff CI upper")

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1:7, 9:12)]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were back transformed using a square-root from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,6:11),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",

            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Fungicide spray schedule efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              se = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )

>>>>

# create data.frame of percent disease severity estimates
results_mv <- cbind(
   data.frame(
      Moderator = c(
         "Intercept / No Spray control",
         "Early",
         "Late",
         "Late+",
         "Recommended",
         "Recommended+"
      ),
      N = k5,
      k = k6
   ),
   backtransform(PMsev_mvPer))

# round the numbers
results_mv[,c(4:6,8:9)] <- round(results_mv[,c(4:6,8:9)], 4)

results_mv <- 
   results_mv %>%
   mutate(
   eff_bar = round(
      1 - estimates, 
      4) * 100,
   eff_CI_high = round(
      1 - CI_lb
   , 4) * 100,
   eff_CI_low = round(
      1 - CI_ub
   , 4) * 100

@@

# rename colnames to give table headings
colnames(results_mv)[c(1:12 )] <-
   c("Moderator",
     "N",
     "k",
     "mu",
     "se",
     "Z",
     "P",
     "CI_{L}",
     "CI_{U}",
     "Efficacy",
     "Eff CI_lower",
     "Eff CI upper")

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), ]) %>%
   align(j = 2:10, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity for each spray schedule treatment. Estimates were back transformed using a inverse logit from the network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4,7:12),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean disease severity",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "Fungicide spray schedule percent efficacy",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval"
         )
      ),
      ref_symbols = letters[c(1:7,4,5)],
      part = "header",
      inline = TRUE
   )%>%
   add_header(Moderator = "",
              N = "",
              k = "",
              mu = "Effect Size",
              se = "Effect Size",
              Z = "Effect Size",
              `CI_{L}` = "Effect Size",
              `CI_{U}` = "Effect Size",
              P  = "Effect Size",
              Efficacy = "PM control",
              `Eff CI_lower` = "PM control",
              `Eff CI upper` = "PM control") %>%
   merge_h( part = "header")%>%
   hline_top(part="all", border = officer::fp_border(color = "black", width = 2) )
